### 2020-03-11 README.Rmd
Try fix structure

```{r echo = FALSE, results='asis'}
descripts <- c(
  "_pkgdown.yml" = "YAML for package website (do not edit)",
  "DESCRIPTION" = "R-package DESCRIPTION (do not edit)",
  "LICENSE.md" = "Project license (do not edit)",
  "NAMESPACE" = "R-package namespace (machine-written)",
  "README.md" = "Read this file to get started!  (do not edit)",
  "README.Rmd" = "R-markdown source for readme.md (human editable)",
  "worcs.Rproj" = "Rstudio project file (do not edit)",
  "docs/" = "Package website (machine-written)",
  "inst/" = "Rstudio project template files  (human editable)",
  "man/" = "R-package documentation (do not edit)",
  "paper/" = "WORCS paper source files (human editable)",
  "R/" = "R-package source code (human editable)",
  "vignettes/" = "R-package vignettes (human editable)"
)
prioritize <- c(
  "README.md",
  "LICENSE.md",
  grep("^(?:(?!/).)*$", names(descripts), value = TRUE, perl = TRUE)
)
prioritize <- unique(prioritize)
f <- list.files(recursive = T)
struc <- f[!grepl("/", f)]
dirs <- f[grepl("/", f)]
dirs <- unique(gsub("/.*$", "/", dirs))

@@

pd <- paste0("%", -1*(max(nchar(levels(struc$file)))+2), "s")
out <- c("```", ".", apply(struc, 1, function(thisrow){
  paste0("├── ", sprintf(pd, thisrow[1]), "<- ", thisrow[2])
}), "```")
cat(out, sep = "\r\n")
```

>>>>

```{r echo = FALSE, results = "asis"}
descripts <- c(
  "_pkgdown.yml" = "YAML for package website (do not edit)",
  "DESCRIPTION" = "R-package DESCRIPTION (do not edit)",
  "LICENSE.md" = "Project license (do not edit)",
  "NAMESPACE" = "R-package namespace (machine-written)",
  "README.md" = "Read this file to get started!  (do not edit)",
  "README.Rmd" = "R-markdown source for readme.md (human editable)",
  "worcs.Rproj" = "Rstudio project file (do not edit)",
  "docs/" = "Package website (machine-written)",
  "inst/" = "Rstudio project template files  (human editable)",
  "man/" = "R-package documentation (do not edit)",
  "paper/" = "WORCS paper source files (human editable)",
  "R/" = "R-package source code (human editable)",
  "vignettes/" = "R-package vignettes (human editable)"
)
prioritize <- c(
  "README.md",
  "LICENSE.md",
  grep("^(?:(?!/).)*$", names(descripts), value = TRUE, perl = TRUE)
)
prioritize <- unique(prioritize)
f <- list.files(recursive = T)
struc <- f[!grepl("/", f)]
dirs <- f[grepl("/", f)]
dirs <- unique(gsub("/.*$", "/", dirs))

@@

pd <- paste0("%", -1*(max(nchar(levels(struc$file)))+2), "s")
out <- c("````", "```", ".", apply(struc, 1, function(thisrow){
  paste0("├── ", sprintf(pd, thisrow[1]), "<- ", thisrow[2])
}), "```", "````")
cat(out, sep = "\r\n")
```
